---
title: "Report Generation using RStudio and Rmarkdown"
subtitle: "What's Rmarkdown, and why should I use it?"
author: Nate Thomas, NH Occupational Health Surveillance Program | Institute on Disability, University of New Hampshire
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  slidy_presentation: default
---

```{r setup = TRUE, echo=FALSE, warning=FALSE, error=FALSE, include=FALSE}
library(tidyverse)
library(knitr)
```

## Purpose

Demonstrate:

1. what Rmarkdown reports are

2. how to make a report using Rmarkdown

## Some common hurdles to report generation and distribution (in no particular order)

- Assuming we know what we want to say, what is the least labor intensive way to get it to the public?

- Making recursive reports (e.g. monthly, yearly) - where the root source of data is structured the same but is updated based on time

- Owning the content, but not the distribution mechanism (having to get IT involved)

## Why Use Rmarkdown?

Concept → Content → Container → Conveyance 

All in one place...

Concept: Perform data investigation in the same interface used to develop the polished product - reducing time cycling between applications and fighting with formatting

Content: Create the actual content of the report directly out of the raw data sets transformations

Container: One file can be used to source the content and output multiple files depending on the preference of the audience (pdf, word, html) - as a pagenated presentation, or flat (scrollable) document

Conveyance: Provide IT with a web-ready document, that can inheret all their predetermined CSS style.

## Examples

### HTML report content:

```{r echo=F, comment=NA}  
readLines("Draft HTML Introduction.Rmd") %>%
  writeLines()
```

### HTML report container:

```{r echo=F}
htmltools::div(
  style = "box-shadow: 5px 5px 6px grey;border: solid;border-color: #EEEEEE; border-width: 5px;",
  htmltools::includeHTML("Draft-HTML-Introduction.html")
)
```

### HTML report conveyance:

https://www.researchondisability.org/ADSC/compendium-table-contents

## Questions? 

