---
title: "Introduction"
params:
  acs_data_year: 2022
  compendium_year: 2024
output:
  html_fragment:
    toc: yes
    lan: "en"
---

```{r include=F, setup = T}
# Update as of 20230117
# script takes in the "SectionX [year].RData" file generated by SectionX v#.Rmd and generates the html compendium.
#year = 2018
library(tidyverse)
library(openxlsx)
library(gt)
library(usmap)
load(paste("Section7 ",params$acs_data_year,".RData",sep=""))
source('table-builders.R')
source('report-helper-functions-html.R')
```

<style type="text/css">

div.main-container {
  max-width: 100% !important;
}

#introduction{
  font-family:"Courier New";
  font-size:12pt
  padding: 0 !important;
  max-width: 100% !important;
}

@media print{
  .pagebreak{
    clear: both;
    page-break-after: always;
  }
  .landscape{
    width: 296mm;
    height: 209mm;
    transform: rotate(270deg) translate(-325mm, 0);
    transform-origin: 0 0;
    margin: 0.5in 0.5in 0.5in 0.5in;
    padding: 0;
  }
}

</style>

# Introduction

Housing is an expense that often uses most of a family’s income. When families spend 30% or more of their income on housing, it is called facing a housing cost burden. In 2022, 4 out of every 10 people with disabilities in Massachusetts had to use 30% or more of their income on housing. Only 2 of every 10 people without disabilities faced this issue. This big difference makes us think about how hard it is for people with disabilities to pay for their homes. 

The map below tells us how much more or less money people with disabilities use for housing compared to those without disabilities in each state of the United States.  

## Housing cost burden for people with disabilities compared to people without disabilities

```{r  echo=F, fig.alt="The map helps us see how people with disabilities spend on housing compared to those without disabilities.  It uses shades to show the difference in risk of experiencing housing cost burden between people with and without disabilities.  In Florida, for example, people with disabilities have only a small increase in risk of experiencing housing cost burden (1.3 times more).  But in North Dakota, people with disabilities are much more likely to experience housing cost burden (2.3 times more), compared to people without disabilities.  The information for this map comes from Table 7.4 Home Environment - Civilians with and without Disabilities Ages 18 to 64 Years Living in the Community Experiencing Housing Cost Burden for the United States and States: 2022", out.width="100%", warning=F, error=F, message=F}
  theme_set(
    theme_void()
  )
  map <- t7.4list$Table %>% 
    mutate(abbr = ST_text %>% str_split_i("/",2)) %>%
    relocate(abbr) %>%
    filter(abbr != "u.s.") %>%
    select(abbr,HS_COST_BRD_RR)  %>%
    mutate(RR_rounded = HS_COST_BRD_RR %>% round(1)) %>%
    mutate(color_breaks1 = ifelse(RR_rounded <= 1.3,"Similar (1.0 to 1.3)",
                                  ifelse(1.3 < RR_rounded & RR_rounded <= 1.6,"1.4 to 1.6",
                                         ifelse(1.6 < RR_rounded & RR_rounded <= 1.9,"1.7 to 1.9",
                                                ifelse(1.9 < RR_rounded & RR_rounded <= 2.2,"2.0 to 2.2",
                                                       ifelse(2.2 < RR_rounded & RR_rounded <= 2.5,"A lot (2.3 to 2.5)",NA))))) %>% 
             factor(levels = c("Similar (1.0 to 1.3)","1.4 to 1.6","1.7 to 1.9","2.0 to 2.2","A lot (2.3 to 2.5)")))
  
  #Get state map data and merge with cost burden data
  states_map <- statepop %>%
    left_join(map,by="abbr")
  
  map_labels1 <- states_map %>%
    mutate(state_label = ifelse(abbr == "MA",HS_COST_BRD_RR %>% round(1),NA)) %>%
    group_by(abbr) %>%
    summarise(state_label = state_label)
  map_labels2 <- states_map %>%
    mutate(state_label = ifelse(abbr == "ND",HS_COST_BRD_RR %>% round(1),NA)) %>%
    group_by(abbr) %>%
    summarise(state_label = state_label)
  map_labels3 <- states_map %>%
    mutate(state_label = ifelse(abbr == "FL",HS_COST_BRD_RR %>% round(1),NA)) %>%
    group_by(abbr) %>%
    summarise(state_label = state_label)
  
  custom_colors <- c("#eef8fe","#aecdeb","#8ca1d3","#8f74b4","#8f308e")
  
  map_gen(states_map,custom_colors,map_labels1,map_labels2,map_labels3)
```

**Map Description**: The map helps us see how people with disabilities spend on housing compared to those without disabilities.  It uses shades to show the difference in risk of experiencing housing cost burden between people with and without disabilities.  In Florida, for example, people with disabilities have only a small increase in risk of experiencing housing cost burden (1.3 times more).  But in North Dakota, people with disabilities are much more likely to experience housing cost burden (2.3 times more), compared to people without disabilities.  The information for this map comes from [Section 7 `r t7.4list$Title`](https://www.researchondisability.org/collection/2024/compendium/section-7#table-7.4-home-environment---civilians-with-and-without-disabilities-ages-18-to-64-years-living-in-the-community-experiencing-housing-cost-burden-for-the-united-states-and-states-2022).

Disability statistics help teach everyone about the lives of people with disabilities. These statistics help check how well government programs work and suggest changes to people who make the rules.

The Annual Disability Statistics Compendium is a collection of important information about people with disabilities in each state of the United States. It includes data from multiple government agencies and programs. The Compendium gathers these statistics together, making it easy for everyone to find and use.

In the Compendium, you can find information like:

 - The total number of people with disabilities in the United States.

 - The number of people with disabilities who are employed.

 - The count of people with disabilities in social insurance programs such as Social Security Disability Insurance.

Along with the Compendium, you can access the following documents: 

 - The Annual Report for People with Disabilities in America: This report uses data from the American Community Survey to show changes in employment, education, health care, and financial stability among people with disabilities over the years.
 
 - The Annual Disability Statistics Compendium Build Your Own Statistics: This is a web interface developed to communicate more granular disability statistics. 

## Notes on the Data

The Compendium is a collection of information gathered from various places like the Social Security Administration (SSA), Veterans Benefits Administration (VBA), the U.S. Census Bureau’s American Community Survey (ACS), and others. Many of these data sources are updated yearly, but not all are. We use the most recent data available.

The Compendium uses the U.S. Census Bureau’s American Community Survey for most of its tables. The ACS uses six questions to figure out if a person has a disability. Each question has two possible answers: “Yes,” or “No.”

Within this data, a response of “Yes” to any of the questions means that the person has a disability. The six types of disability are vision, hearing, cognitive, ambulatory, self-care, and independent living.

```{r echo=F, fig.alt="Six Questions include in the American Community Survey (ACS)",results='asis'}
tab_html <- tibble("Disability Type" = c("Hearing","Vision","Cognitive","Ambulatory","Self-Care","Independent Living"),
           "Age Group" = c("All","All","5 years and older","5 years and older","5 years and older","15 years and older"),
           Question = c("Is this person deaf, or do they have serious difficulty hearing?", 
                        "Is this person blind, or do they have serious difficulty seeing even when wearing glasses?", 
                        "Does this person have a hard time focusing, remembering, or making decisions because of a physical, mental, or emotional condition?",
                        "Does this person have a hard time walking or going upstairs?",
                        "Does this person have a hard time getting dressed or bathing?",
                        "Does this person have a hard time doing tasks alone, like going to the doctor’s office or shopping, due to physical, mental, or emotional conditions?")) %>%
  gt(rowname_col = "Disability Type")|>
    tab_stubhead(label = "Disability Type") |>
    tab_options(
      table.font.size = 16, footnotes.font.size = 16, source_notes.font.size = 16) |>    
      opt_table_font(
        font = list("Courier new")) |>
    tab_style(style = "vertical-align:top", cells_column_labels()) 

id_correction_fn(tab_html,file = 'intro.html')
```

Sometimes, the categories we use don't give us all the details we might want. For example, the cognitive disability category doesn’t tell us whether the disability is related to a brain injury or a developmental disability.

## New This Year

Understanding how many people are in a group is important, but it's also important to know how certain we are about that information. Survey data rely on the answers of some people to predict the total population in each group. For this reason, all statistics are estimates or best predictions. We also provide a second number for each survey estimate called the margin of error that can be used to calculate the range of numbers possible for any single estimate. The margin of error can help you understand the uncertainty in the collected information. For example, the larger the margin of error, the more likely it is that our best guess is higher or lower than the true number.  

To make the comparison between two groups (people with and without disabilities) clearer, in most cases, we have added relative ratios to our tables. Relative ratios make it easier to compare groups of different sizes. If the relative ratio is higher than one, in the Compendium, this generally means that a bigger group of people with disabilities are experiencing something compared to people without disabilities. For example, we could use these ratios to describe the differences between people with and without disabilities who spend more than 30% of their income on housing. Imagine the relative ratio is 1.374 for this measure in Massachusetts. This would mean that for every 1,000 people without disabilities who are facing housing challenges, about 1,374 people with disabilities are in a similar situation.

## Additional Resources

 - You can find individual reports at https://disabilitycompendium.org/.

 - You can access our FAQ (frequently asked questions) page at https://disabilitycompendium.org/faq

 - If you need help finding or interpreting specific statistics, please contact us by emailing us at disability.statistics@unh.edu or calling (866)-538-9521.


Suggested Citation. Thomas, N., Paul, S., Bach, S., & Houtenville, A. (`r params$compendium_year`). Annual Disability Statistics Compendium: `r params$compendium_year` Durham, NH: University of New Hampshire, Institute on Disability.

